### 2010-04-14 doc/tech_doc/client/client_technical.tex
Switching documents to bibliography style which is supposed to be present in latex distributions. Fixes in some documents and build procedures.
knowarc1 changes in every files
New testing machine: https://interop.grid.niif.hu:2010/arex-x509

%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {KnowARC collaboration},
  pdftitle = {libarcclient},
  pdfsubject = {A Client Library for ARC},
  pdfkeywords = {ARC,client,library},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\newcommand{\libarcclient}{libarcclient}
\newcommand{\ACC}{\texttt{ACC}}
\newcommand{\ACCConfig}{\texttt{ACCConfig}}
\newcommand{\Config}{\texttt{Config}}
\newcommand{\Broker}{\texttt{Broker}}
\newcommand{\Random}{\texttt{Random}}
\newcommand{\Benchmark}{\texttt{Benchmark}}
\newcommand{\FastestQueueBroker}{\texttt{FastestQueueBroker}}
\newcommand{\PythonBroker}{\texttt{PythonBroker}}
\newcommand{\Data}{\texttt{Data}}
\newcommand{\ClientInterface}{\texttt{ClientInterface}}
\newcommand{\ClientTCP}{\texttt{ClientTCP}}
\newcommand{\ClientHTTP}{\texttt{ClientHTTP}}
\newcommand{\ClientSOAP}{\texttt{ClientSOAP}}
\newcommand{\ExecutionTarget}{\texttt{ExecutionTarget}}
\newcommand{\Job}{\texttt{Job}}
\newcommand{\JobController}{\texttt{JobController}}
\newcommand{\JobDescription}{\texttt{JobDescription}}
\newcommand{\JobSupervisor}{\texttt{JobSupervisor}}
\newcommand{\Loader}{\texttt{Loader}}
\newcommand{\Logger}{\texttt{Logger}}
\newcommand{\TargetGenerator}{\texttt{TargetGenerator}}
\newcommand{\TargetRetriever}{\texttt{TargetRetriever}}
\newcommand{\Sandbox}{\texttt{Sandbox}}
\newcommand{\Submitter}{\texttt{Submitter}}
\newcommand{\URL}{\texttt{URL}}
\newcommand{\UserConfig}{\texttt{UserConfig}}
\newcommand{\XML}{\texttt{XML}}
\newcommand{\XMLNode}{\texttt{XMLNode}}
\newcommand{\NST}[1]{\normalsize{\textnormal{#1}}}
% parbox with centered text and vertical padding. It provides fixed width table-cells holding multiline centered text. \mlccell{<width>}{<text>}
% Use in a tabular environment as \mlccell{10em}{line 1 \linebreak line 2 \linebreak line 3, etc.}
\newcommand{\mlccell}[2]{\parbox{#1}{\vspace{0.4\baselineskip}\centering #2 \vspace{0.4\baselineskip}}}
\newcommand{\n}{\linebreak}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}

@@

\begin{shaded}
\begin{verbatim}
<CacheCheck>
   <TheseFilesNeedToCheck>
       <FileURL>http://knowarc1.grid.niif.hu/storage/Makefile</FileURL>
       <FileURL>ftp://download.nordugrid.org/test/README</FileURL>
   </TheseFilesNeedToCheck>
</CacheCheck>
\end{verbatim}
\end{shaded}

@@

\begin{shaded}
\begin{verbatim}
<CacheCheckResponse>
   <CacheCheckResult>
   <Result>
         <FileURL>http://knowarc1.grid.niif.hu/storage/Makefile</FileURL>
         <ExistInTheCache>true</ExistInTheCache>
         <FileSize>190</FileSize>
   </Result>
   <Result>
         <FileURL>ftp://download.nordugrid.org/test/README</FileURL>
         <ExistInTheCache>true</ExistInTheCache>
         <FileSize>176</FileSize>
   </Result>
  </CacheCheckResult>
</CacheCheckResponse>
\end{verbatim}
\end{shaded}

>>>>

%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {KnowARC collaboration},
  pdftitle = {libarcclient},
  pdfsubject = {A Client Library for ARC},
  pdfkeywords = {ARC,client,library},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\usepackage[numbers]{natbib}
\bibliographystyle{plainnat}
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\newcommand{\libarcclient}{libarcclient}
\newcommand{\ACC}{\texttt{ACC}}
\newcommand{\ACCConfig}{\texttt{ACCConfig}}
\newcommand{\Config}{\texttt{Config}}
\newcommand{\Broker}{\texttt{Broker}}
\newcommand{\Random}{\texttt{Random}}
\newcommand{\Benchmark}{\texttt{Benchmark}}
\newcommand{\FastestQueueBroker}{\texttt{FastestQueueBroker}}
\newcommand{\PythonBroker}{\texttt{PythonBroker}}
\newcommand{\Data}{\texttt{Data}}
\newcommand{\ClientInterface}{\texttt{ClientInterface}}
\newcommand{\ClientTCP}{\texttt{ClientTCP}}
\newcommand{\ClientHTTP}{\texttt{ClientHTTP}}
\newcommand{\ClientSOAP}{\texttt{ClientSOAP}}
\newcommand{\ExecutionTarget}{\texttt{ExecutionTarget}}
\newcommand{\Job}{\texttt{Job}}
\newcommand{\JobController}{\texttt{JobController}}
\newcommand{\JobDescription}{\texttt{JobDescription}}
\newcommand{\JobSupervisor}{\texttt{JobSupervisor}}
\newcommand{\Loader}{\texttt{Loader}}
\newcommand{\Logger}{\texttt{Logger}}
\newcommand{\TargetGenerator}{\texttt{TargetGenerator}}
\newcommand{\TargetRetriever}{\texttt{TargetRetriever}}
\newcommand{\Sandbox}{\texttt{Sandbox}}
\newcommand{\Submitter}{\texttt{Submitter}}
\newcommand{\URL}{\texttt{URL}}
\newcommand{\UserConfig}{\texttt{UserConfig}}
\newcommand{\XML}{\texttt{XML}}
\newcommand{\XMLNode}{\texttt{XMLNode}}
\newcommand{\NST}[1]{\normalsize{\textnormal{#1}}}
% parbox with centered text and vertical padding. It provides fixed width table-cells holding multiline centered text. \mlccell{<width>}{<text>}
% Use in a tabular environment as \mlccell{10em}{line 1 \linebreak line 2 \linebreak line 3, etc.}
\newcommand{\mlccell}[2]{\parbox{#1}{\vspace{0.4\baselineskip}\centering #2 \vspace{0.4\baselineskip}}}
\newcommand{\n}{\linebreak}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}

@@

\begin{shaded}
\begin{verbatim}
<CacheCheck>
   <TheseFilesNeedToCheck>
       <FileURL>http://example.org/storage/Makefile</FileURL>
       <FileURL>ftp://download.nordugrid.org/test/README</FileURL>
   </TheseFilesNeedToCheck>
</CacheCheck>
\end{verbatim}
\end{shaded}

@@

\begin{shaded}
\begin{verbatim}
<CacheCheckResponse>
   <CacheCheckResult>
   <Result>
         <FileURL>http://example.org/storage/Makefile</FileURL>
         <ExistInTheCache>true</ExistInTheCache>
         <FileSize>190</FileSize>
   </Result>
   <Result>
         <FileURL>ftp://download.nordugrid.org/test/README</FileURL>
         <ExistInTheCache>true</ExistInTheCache>
         <FileSize>176</FileSize>
   </Result>
  </CacheCheckResult>
</CacheCheckResponse>
\end{verbatim}
\end{shaded}
